%%%%%%%%%%%%%%%%%
% This is a two-column CV template based on moderncv.cls
% (v1.0, May 16, 2024) written by Genki Ogaki (rockstarogk@gmail.com). Compiles with XeLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

% environment
\documentclass[10pt,a4paper,hidelinks,unicode]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}
\usepackage{tabularx}
\usepackage{mathpazo}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}

% macro
\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[5][1.5mm]{
    \subsection{#2} \vspace{-1.5mm}
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #3} & {\itshape #4, #5}
    \end{tabularx}
    \par\addvspace{#1}
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

\newcommand*{\scoreentry}[3][2.5mm]{
    {\bfseries #2} \\
    {\itshape #3}
    \par\addvspace{#1}
}

% preamble
\firstname{Rana Nilesh}
\familyname{Vanikar}
\address{Pune, Maharashtra}{}

% document
\begin{document}
\maketitle
\vspace{-10.0mm}
\begin{tabularx}{\textwidth}{C C C}
    \emailsymbol\enspace \href{mailto:rana.vanikar@gmail.com}{rana.vanikar@gmail.com} & \mobilephonesymbol\enspace \href{tel:+918380099014}{+91 8380099014} & \faLinkedin\enspace \href{https://www.linkedin.com/in/rana-vanikar/}{linkedin.com/in/rana-vanikar}
\end{tabularx}
\vspace{-5.0mm}

% left column
\begin{minipage}[t]{0.62\textwidth}
\section{EXPERIENCE}
\experienceentry{Cybage Software}{Application Security Tester (Intern)}{Dec 2023 - Feb 2024}{Kalyani Nagar, Pune, Maharashtra}

\textbf{Application Security Testing}
\begin{itemize}
    \item Conducted Static Application Security Testing (SAST) using SonarQube.
    \item Performed Software Composition Analysis (SCA) with Cyclone DX and Dependency Track.
    \item Executed Dynamic Application Security Testing (DAST) and Vulnerability Assessment and Penetration Testing (VAPT) using industry-standard tools and followed the OWASP Web Security Testing guide.
    \item Set up and configured tools using Docker and Proxmox, including creating virtual environments for testing.
    \item Prepared comprehensive security testing reports detailing findings and recommendations.
\end{itemize}
\vspace{2.0mm}

\experienceentry{PICT CyberCell}{Technical Head}{Jul 2023 - Present}{PICT}

\textbf{Technical Leadership and Event Management}
\begin{itemize}
    \item Led technical operations for events, including the deployment and management of websites and vulnerable VMs for Capture the Flag (CTF) competitions.
    \item Managed network monitoring and security for major events, such as the CTF event conducted by IIT Bombay Trust Labs and HSBC.
    \item Conducted sessions and seminars on networking and cybersecurity tools, including Nmap and Wireshark.
\end{itemize}
\vspace{2.0mm}

\experienceentry{PICT Automobile Club - Torqscrew}{Electrical Head}{Mar 2022 - Mar 2023}{PICT}

\textbf{Electrical System Design for Electric Go-Kart}
\begin{itemize}
    \item Designed and implemented electrical systems, including battery management, motor controller integration, and wiring harnesses.
    \item Ensured the safety and reliability of the electrical components and systems.
    \item Managed the integration of small electronic components like tail lights and safety switches.
\end{itemize}
\vspace{2.0mm}

\section{PROJECTS}

\textbf{IoT Powered Power Over Ethernet (PoE) Device}
\begin{itemize}
    \item Developed an IoT-powered PoE injector with integrated sensors and a microcontroller to measure and report power transmission data to a dashboard.
    \item Created a PoE extractor for devices that do not support PoE, enabling them to be powered over the network.
\end{itemize}
\vspace{2.0mm}

\end{minipage}
\hfill
% right column
\begin{minipage}[t]{0.35\textwidth}
\section{SUMMARY}
As a passionate cybersecurity and networking enthusiast, I am an undergraduate engineering student at PICT specializing in Electronics and Telecommunications (EnTC). With hands-on experience in IT infrastructure, Linux and Windows systems, networking devices, and cloud platforms, I am dedicated to applying my cybersecurity skills to protect and optimize network systems. Currently seeking internships in cybersecurity, networking, DevOps, and cloud domains to leverage my knowledge and contribute to a forward-thinking organization.

\section{SKILLS}
\begin{tabularx}{\textwidth}{>{\bfseries}l@{\hskip 3.5mm}L}
Cybersecurity & Network Security, Web App Security \\
Programming Languages & Python, C++ \\
DBMS & MySQL \\
Computer Networking & Networking Gear\\
DevOps & Docker \\
Cloud Computing & AWS, GCP \\
Other Skills & Digital Marketing \\
Languages & English, Hindi, Marathi \\
\end{tabularx}

\section{EDUCATION}
\educationentry{Bachelor of Engineering - Electronics and Tele-Communications (EnTC)}{Pune Institute of Computer Technology (PICT)}{Dec 2021 - Jun 2025 (Tentative)}{}
CGPA: 8.52/10

\educationentry{Higher Secondary Certificate (HSC)}{Sir Parshurambhau College}{2019 - 2021}{}
Percentage: 82.3\%

\educationentry{CBSE}{Millennium National School}{2019}{Pune, Maharashtra}
Percentage: 92.8\%



\end{minipage}

\end{document}
