\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Rana N. Vanikar}}\\
	Pune, Maharashtra, India $\cdot$ rana.vanikar@outlook.com $\cdot$ +91 8380099014 $\cdot$ www.linkedin.com/in/rana-vanikar/\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Pune Institute of Computer Technology (SPPU)}\hfill Pune, Maharashtra, India\\
BE Electronics and Telecommunications \textit{GPA: 8.76} \hfill Dec 2021 - July 2025 (Expected)\\
\vspace{2mm}
\textbf{SP College Pune}\hfill Pune, Maharashtra, India\\
High School (HSC) PCM \textit{GPA: 82.83\%} \hfill June 2019 - May 2021\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Uniken INC} \hfill Pune, Maharashtra, India\\
\textit{Intern - Mobile Application Security Tester} \hfill Aug 2024 - Nov 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Conducted static \& dynamic analysis of Android applications using industry-standard tools.
	\item Evaluated application vulnerabilities and reported security flaws with remediation steps.
	\item Applied OWASP Mobile Top 10 techniques to assess security vulnerabilities in Android applications.
\end{itemize}
\textbf{Cybage Software} \hfill Pune, Maharashtra, India\\
\textit{Intern - Cybersecurity} \hfill Dec 2023 - Feb 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Automated SAST \& SCA integration into CI/CD pipelines, optimizing security workflows and enhancing DevSecOps practices
	\item Performed manual DAST and API penetration testing following OWASP standards.
	\item Compiled security testing reports and recommended fixes to improve web application security.
\end{itemize}
\textbf{PICT CyberCell} \hfill PICT, Pune\\
\textit{Technical Head} \hfill July 2023 - Aug 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Conducted workshops on advanced topics such as DevSecOps, Computer Networking and Network Security
	\item Deployed and automated cloud infrastructure for CTF events and workshops, ensuring seamless operations.
	\item Engineered scalable, secure network access solutions for IITB+HSBC CTF events, ensuring high availability and security.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming and Scripting: & Python, JavaScript, C/C++, Bash                                     \\
	Essentials:                & DBMS(MySQL), OS, Networking, DevOps, CI/CD, Cloud Computing         \\
	Tools and Services:        & Ansible, Docker, Git, Zabbix, Grafana, Kubernetes                   \\
	Cloud:                     & AWS, Azure, DigitalOcean, Proxmox                                   \\
	Cybersecurity:             & OWASP, MITRE ATT\&CK, Bug Hunting, Incident Response, Wazuh, SPLUNK \\
\end{tabular}
\vspace{2mm}

\header{Projects}
{\textbf{Home Lab}} {\sl Routers, Layer 3 switches, wireless access points, Proxmox node, Ansible, Zabbix} \\
Built and manage a home lab with virtual machines and containers for hands-on DevOps and DevSecOps experimentation. Automated infrastructure management using Ansible, and monitoring system performance using Grafana, InfluxDB and RestAPI.\\
\vspace*{2mm}
{\textbf{AI Powered Deep Packet Analyzer}} {\sl Python, AI/ML, Scapy, Wireshark, L3 Managed Switch} \\
Developing an AI-driven network security model for real-time packet inspection and anomaly detection using Python, Scapy, and Wireshark. The system classifies packets by signatures, protocols, and traffic patterns to detect threats proactively. A related research paper, highlighting AI’s role in cybersecurity, is set for publication in Springer LNNS.\\
\vspace*{2mm}
{\textbf{IoT Powered Power Over Ethernet Injector and Extractor}} {\sl ESP32, ACS712, Azure, Grafana, InfluxDB} \\
Developed an IoT-enabled Power over Ethernet (PoE) system with real-time power monitoring and a cloud-based dashboard for data visualization. Integrated seamlessly with existing network infrastructure, enabling real-time monitoring.\\
\vspace*{2mm}
{\textbf{Multiple 3D Printer Orchestration}} {\sl RaspberryPI, AWS (For VPN Tunnel), Servo Motors, Ender3 3D printers} \\
Developed a system for managing multiple 3D printers with centralized control and secure remote access. Automated monitoring and job scheduling, optimizing efficiency and reducing manual intervention.\\
\vspace*{2mm}



\ 
\end{document}